Example of Market Simulator Dasbhaord

### 2021-09-22 README.Rmd
Add instructions for ignoring Dropbox files

Because the posterior draws from the models are large and take forever to make, we've saved the results as `.rds` files. However, because those files are fairly big and we don't want to track them with git, we've stored them at this project's [OSF page](https://osf.io/r59xz/) in [OSF's internal storage system](https://osf.io/r59xz/files/). Running `targets::tar_make(starts_with("file_"))` (or just `targets::tar_make()` in general) will trigger a function (`get_from_osf()`) that will automatically download all the `.rds` files and place them in `data/raw_data/posterior_draws`, which is not tracked by git (and which should be set to not sync in Dropbox).

>>>>

Because the posterior draws from the models are large and take forever to make, we've saved the results as `.rds` files. However, because those files are fairly big and we don't want to track them with git, we've stored them at this project's [OSF page](https://osf.io/r59xz/) in [OSF's internal storage system](https://osf.io/r59xz/files/). Running `targets::tar_make(starts_with("file_"))` (or just `targets::tar_make()` in general) will trigger a function (`get_from_osf()`) that will automatically download all the `.rds` files and place them in `data/raw_data/posterior_draws`, which is not tracked by git.

If you're part of the research team and using Dropbox, make sure you make it so that Dropbox ignores the `posterior_draws` folder. There are [complete instructions for doing that here](https://help.dropbox.com/files-folders/restore-delete/ignored-files). In short, run one of these commands in your terminal:

```sh
# On macOS
cd path/to/this/project
xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws

# On Windows (with PowerShell)
cd path/to/this/project
Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1
```

The icon next to the `posterior_draws` folder should then change to a gray minus sign, which means that the folder is being ignored.
